DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-16 paper/conclusion.tex
Changes to paper
Minor changes to paper

Despite the complexity of the neural network, DeepPicar uses a
low-cost Raspberry Pi 3 quad-core computer as a sole computing
resource. We systematically analyzed the real-time characteristics of
the Pi 3 platform in the context of deep-learning based real-time
control appilcations, with a special emphasis on real-time deep neural
network inferencing.
We also evaluated other, more powerful, embedded computing
platforms to better understand achievable real-time performance of
DeepPicar's deep-learning based control system and the impact of
computing hardware architectures.
We find all tested embedded platforms, including the Pi3, are capable
of supporting deep-learning based real-time control, from 20 Hz up to
100 Hz, depending on the platform and its system
configuration. However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.

>>>>

Despite the complexity of the neural network, DeepPicar uses a
low-cost Raspberry Pi 3 quad-core computer as its sole computing
resource. We systematically analyzed the real-time characteristics of
the Pi 3 platform in the context of deep-learning based real-time
control appilcations, with a special emphasis on real-time deep neural
network inferencing.
We also evaluated other, more powerful, embedded computing
platforms to better understand achievable real-time performance of
DeepPicar's deep-learning based control system and the impact of
computing hardware architectures.
We find all tested embedded platforms, including the Pi 3, are capable
of supporting deep-learning based real-time control, from 20 Hz up to
100 Hz, depending on the platform and its system
configuration. However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.
